Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

\section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
None of the surveyed tools were suitable for our definitions of refactorable clones. Therefore, we built a new tool, CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.} This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}. In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones. In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.

@@

\subsection{Survey of existing clone detection tools}\label{sec:survey}
%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
To investigate the impact of the definitions introduced in Sec.~\ref{sec:research}, we need a tool to detect refactorable clones according to these definitions. We conducted a short survey on (recent) clone detection tools to detect such clones that can be refactored. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze a popular object-oriented programming language. Next, we formulate the following four criteria by which we analyze these tools:
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method level clones. We want to perform an analysis of all clones in projects to get a complete overview.
\item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of the surveyed clone detection tools.
\item \textbf{Can analyze resolved symbols.} When detecting the clones proposed in Sec.~\ref{sec:research}, it is important that we can analyze resolved symbols (for instance a type reference).
\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in Sec.~\ref{sec:research}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.). The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
\end{enumerate}

>>>>

\section{A tool for automatic clone refactoring}\label{sec:clonerefactor}

To automatically refactor a large set of clones, we first need tool able to detect refactorable clones, as defined in Sec.~\ref{sec:research}.  We formulate the following four c required by such :
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method level clones. We want to perform an analysis of all clones in projects to get a complete overview.
\item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of the surveyed clone detection tools.
\item \textbf{Can analyze resolved symbols.} When detecting the clones proposed in Sec.~\ref{sec:research}, it is important that we can analyze resolved symbols (for instance a type reference).
\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in Sec.~\ref{sec:research}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.). The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
\end{enumerate}

@@

None of the surveyed tools were suitable for our definitions of refactorable clones. Therefore, we built a new tool, CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.} This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}. In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones. In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.

% \subsection{Survey of existing clone detection tools}\label{sec:survey}
%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
